---
title: "IEAP-Series03-Assignment"
author: "Sarah Durand, Gaia Gassiole, Vidusha Thebuwana"
date: today
format:
  html: default
  pdf: default
---
**GitHub repository:** <https://github.com/sdurand875-spec/IEAP-Series03-RStudio>

# **IEAP-Rstudio-Series03**

### Data wrangling and ANOVA

# **1 ANOVA: Analysis of variance**

### 1.1 **Think before coding**

The scientific question is:

- Is the effect of difficulty different in patients with stroke compared to healthy?

  - How do you visualize this?

    - ggplot

  - Is there a significant difference?

    - ANOVA?

  - What sentence should we write to state this result in a report?

## **1.2 What library to answer the above questions?**

### Load library

```{r}
library(tidyverse)
library(ez)
```

## **1.3 Data reorganization**

## Load data

```{r}
data <- read.table(
  text = readLines("data/Results.txt"),
  header = TRUE,
  sep = "",
  stringsAsFactors = TRUE
)

head(data)
```

We need to reorganize the data.

To do so, we count the number of data points for each combination of factors to check if there is missing data.

The following function looks for every unique combination of GROUP and ID in the dataset and tallies up the number of rows for each pair. It automatically generates a new column named n that contains these totals. we do that to check if the number of rows is the same for every combination.

```{r}
data_counts <- data %>%
  count(GROUP, ID)

print(data_counts)
```

For item 9 "pp ID3 400", the number of rows does not match the rest of the group 'PP', so we need to delete ID3. The fact that some data are missing is explained by some stroke patients not being able to perform the test at ID3.

```{r}
data %>%
  filter(ID != "ID3") %>%
  count(GROUP, ID)

```

Now let's look at other columns such as REP.

```{r }
data %>% 
  filter(ID != "ID3") %>%
  count(REP)
```

The number of repetitions for R3 is half the number of R1 and R2. Therefore, we delete R3 data from our data frame.

```{r}

data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  count(GROUP, ID, REP)
```

We created a tibble 3 × 2 to look for the number of participants in each group.

```{r}
data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  distinct(GROUP, SUBJ) %>%
  count(GROUP, name='count')
```

Now we create a new variable to store the cleaned data.

```{r}
data_clean <- data %>% 
  filter(ID != "ID3") %>% 
  filter(REP != "R3")
head(data_clean)
```

{{< include Section/section_1_gaia.qmd >}}

{{< include Section/section_2_vidusha.qmd >}}

{{< include Section/section_3_sarah.qmd >}}

# 1.7 Discuss the differences with the article
Our results are a little different from those of the article, because our method is simpler. We removed ID3 and R3 (missing data), we calculated the regressions on all the trials together and not for each participant, and we used error bars of ± 0.5 standard deviation.

However, the conclusions are the same. In the three groups, movement time increases with difficulty (Fitts' law), but this increase is much stronger in the pp group (≈ 0.90 s/bit) than in the ap and cp groups (≈ 0.12 to 0.17 s/bit). The ANOVA confirms this with a significant GROUP × ID interaction.

The conclusions stay the same because the effect is very large: the differences in method change the exact values, but not the meaning of the result. However, with only two difficulty levels, we cannot check that the relationship is really linear.

{{< include workflow.qmd >}}

{{< include challenges.qmd >}}



# Data sources and references

### Data source

- `Results.txt`: movement time data from a Fitts' pointing task performed by three groups of participants (ap, cp, pp), provided by Denis Mottet for the IEAP RStudio course. Available at: <https://moodle.umontpellier.fr/course/view.php?id=41022>

### Scientific references

- Mottet, D., van Dokkum, L. E. H., Froger, J., Gouaïch, A., & Laffont, I. (2017). Trajectory formation principles are the same after mild or moderate stroke. *PLoS ONE*, 12(3), e0173674. <https://doi.org/10.1371/journal.pone.0173674>
- Fitts, P. M. (1954). The information capacity of the human motor system in controlling the amplitude of movement. *Journal of Experimental Psychology*, 47(6), 381–391. <https://doi.org/10.1037/h0055392>

### Software and R packages

- R Core Team (2025). *R: A language and environment for statistical computing*. R Foundation for Statistical Computing. <https://www.R-project.org/>
- Wickham, H., et al. (2019). Welcome to the tidyverse. *Journal of Open Source Software*, 4(43), 1686. <https://doi.org/10.21105/joss.01686>
- Lawrence, M. A. *ez: Easy analysis and visualization of factorial experiments*. R package. <https://CRAN.R-project.org/package=ez>
- Müller, K. *here: A simpler way to find your files*. R package. <https://CRAN.R-project.org/package=here>


# Checklist

We used the following checklist to make sure that our work meets all the requirements and grading criteria of the assignment.

### Report content

- [x] Authors and date in the header
- [x] Clickable link to our public GitHub repository
- [x] Analysis of our team's Git workflow strategy
- [x] Analysis of the challenges encountered and lessons learned
- [x] Complete code and answers to all the questions (1.1 to 1.7)
- [x] Data sources (with their URLs)
- [x] Scientific references (with their DOIs)
- [x] Checklist used to meet the grading criteria

### ANOVA pipeline and Quarto document

- [x] Clear ANOVA pipeline, with an explanation of each step
- [x] Master Quarto document (`IEAP-Series03-Rstudio.qmd`) in which the sub-documents are included when rendering
- [x] Graph similar to Figure 3 of the article, with regression lines and equations
- [x] Graph exported as an 8 × 6 inch PDF file

### GitHub repository

- [x] Public repository named `IEAP-Series03-RStudio`
- [x] `main` branch up to date
- [x] Clear and complete `README.md`
- [x] `LICENSE` file
- [x] Rendered PDF file of the report
- [x] Clear Git history with meaningful commit messages
- [x] At least one commit per question of the report
- [x] Use of branches to work on different questions in parallel, merged into `main` with Pull Requests
