---
title: "IEAP-Series03-Assignment"
author: "Sarah Durand, Gaia Gassiole, Vidusha Thebuwana"
date: today
format:
  html: default
  pdf: default
---
**GitHub repository:** <https://github.com/sdurand875-spec/IEAP-Series03-RStudio>

# **IEAP-Rstudio-Series03**

### Data wrangling and ANOVA

# **1 ANOVA: Analysis of variance**

### 1.1 **Think before coding**

The scientific question is:

- Is the effect of difficulty different in patients with stroke compared to healthy?

  - How do you visualize this?

    - ggplot

  - Is there a significant difference?

    - ANOVA?

  - What sentence should we write to state this result in a report?

## **1.2 What library to answer the above questions?**

### Load library

```{r}
library(tidyverse)
library(ez)
```

## **1.3 Data reorganization**

## Load data

```{r}
data <- read.table(
  text = readLines("data/Results.txt"),
  header = TRUE,
  sep = "",
  stringsAsFactors = TRUE
)

head(data)
```

We need to reorganize the data.

To do so, we count the number of data points for each combination of factors to check if there is missing data.

The following function looks for every unique combination of GROUP and ID in the dataset and tallies up the number of rows for each pair. It automatically generates a new column named n that contains these totals. we do that to check if the number of rows is the same for every combination.

```{r}
data_counts <- data %>%
  count(GROUP, ID)

print(data_counts)
```

For item 9 "pp ID3 400", the number of rows does not match the rest of the group 'PP', so we need to delete ID3. The fact that some data are missing is explained by some stroke patients not being able to perform the test at ID3.

```{r}
data %>%
  filter(ID != "ID3") %>%
  count(GROUP, ID)

```

Now let's look at other columns such as REP.

```{r }
data %>% 
  filter(ID != "ID3") %>%
  count(REP)
```

The number of repetitions for R3 is half the number of R1 and R2. Therefore, we delete R3 data from our data frame.

```{r}

data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  count(GROUP, ID, REP)
```

We created a tibble 3 × 2 to look for the number of participants in each group.

```{r}
data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  distinct(GROUP, SUBJ) %>%
  count(GROUP, name='count')
```

Now we create a new variable to store the cleaned data.

```{r}
data_clean <- data %>% 
  filter(ID != "ID3") %>% 
  filter(REP != "R3")
head(data_clean)
```

{{< include Section/section_1_gaia.qmd >}}

{{< include Section/section_2_vidusha.qmd >}}

{{< include Section/section_3_sarah.qmd >}}

{{< include workflow.qmd >}}

{{< include challenges.qmd >}}

