# 1.3 Data reorganization

## **1.2 What library to answer the above questions?**

### Load library

```{r Load the libraries}
library(tidyverse)
library(ez)
```

## **1.3 Data reorganization**

## Load data

```{r Load data}
#data <- read_csv("data/Results.txt", delimiter = " ")
data <- read.table("../data/Results.txt", header = TRUE, sep = "" , stringsAsFactors = TRUE)
```

We need to reorganize the data.

To do so, we count the number of data points for each combination of factors to check if there is missing data.

The following function looks for every unique combination of GROUP and ID in the dataset and tallies up the number of rows for each pair. It automatically generates a new column named n that contains these totals. we do that to check if the number of rows is the same for every combination.

```{r Count data}
data_counts <- data %>%
  count(GROUP, ID)

print(data_counts)
```

For item 9 "pp ID3 400", the number of rows does not match the rest of the group 'PP', so we need to delete ID3. The fact that some data are missing is explained by some stroke patients not being able to perform the test at ID3.

```{r}
data %>%
  filter(ID != "ID3") %>%
  count(GROUP, ID)

```

Now let's look at other columns such as REP.

```{r }
data %>% 
  filter(ID != "ID3") %>%
  count(REP)
```

The number of repetitions for R3 is half the number of R1 and R2. Therefore, we delete R3 data from our data frame.

```{r}

data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  count(GROUP, ID, REP)
```

We created a tibble 3 × 2 to look for the number of participants in each group.

```{r}
data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  distinct(GROUP, SUBJ) %>%
  count(GROUP, name='count')
```

Now we create a new variable to store the cleaned data.

```{r}
data_clean <- data %>% 
  filter(ID != "ID3") %>% 
  filter(REP != "R3")
print(data_clean)
```


## Run the ANOVA 

```{r}
anova_results <- ezANOVA(
  data = data_clean,
  dv = .(MovementTime),# dependent variable
  wid = .(SUBJ),# to recognize each participant
  within = .(ID),# within-subject factor
  between = .(GROUP), # between-subject factor 
  detailed = FALSE
)

anova_results$ANOVA
```
ANOVA p-value:

We format the p-value to avoid scientific notation and see the full number. That way, it's easier to interpret the results.
```{r}
format(anova_results$ANOVA$p, scientific = FALSE, digits = 10)
```
The ANOVA revealed significant main effects of GROUP and ID, as well as a significant GROUP × ID interaction, with all p-values below 0.01.

Detailed ANOVA results: 

Effect of the GROUP: Movement Time is different between the three groups (p < 0.01).

Effect of ID: Movement Time is different between the two IDs (p < 0.01).

Interaction effect GROUPxID: The effect of ID on Movement Time depends on the GROUP (p < 0.01).

## Plot the ANOVA



