## **1.2 What library to answer the above questions?**

### Load library

```{r Load the libraries}
library(tidyverse)
library(ez)
```

## **1.3 Data reorganization**

## Load data

```{r Load data}
data <- read.table("../data/Results.txt", header = TRUE, sep = "" , stringsAsFactors = TRUE)
```

We need to reorganize the data.

To do so, we count the number of data points for each combination of factors to check if there is missing data.

The following function looks for every unique combination of GROUP and ID in the dataset and tallies up the number of rows for each pair. It automatically generates a new column named n that contains these totals. we do that to check if the number of rows is the same for every combination.

```{r Count data}
data_counts <- data %>%
  count(GROUP, ID)

print(data_counts)
```

For item 9 "pp ID3 400", the number of rows does not match the rest of the group 'PP', so we need to delete ID3. The fact that some data are missing is explained by some stroke patients not being able to perform the test at ID3.

```{r}
data %>%
  filter(ID != "ID3") %>%
  count(GROUP, ID)

```

Now let's look at other columns such as REP.

```{r }
data %>% 
  filter(ID != "ID3") %>%
  count(REP)
```

The number of repetitions for R3 is half the number of R1 and R2. Therefore, we delete R3 data from our data frame.

```{r}

data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  count(GROUP, ID, REP)
```

We created a tibble 3 × 2 to look for the number of participants in each group.

```{r}
data %>% 
  filter(ID != "ID3") %>%
  filter(REP != "R3") %>%
  distinct(GROUP, SUBJ) %>%
  count(GROUP, name='count')
```

Now we create a new variable to store the cleaned data.

```{r}
data_clean <- data %>% 
  filter(ID != "ID3") %>% 
  filter(REP != "R3")
print(data_clean)
```

# 1.4 Run the linear regression by GROUP

First let's check the data types of each column. Linear regression requires a number not strings.

```{r }
str(data_clean)
```

Since ID is a categorical variable and it is better to run the actual numeric values before fitting to the linear model. Since ID1 was 3.8 and ID2 was 5.43 the data can be manipulated as follows:

```{r}
data_reg <- data_clean %>%
  mutate(ID_num = case_when(
    ID == "ID1" ~ 3.8,
    ID == "ID2" ~ 5.43
  ))

```

Now that data type is stored properly. Let's run the linear model.

```{r}

models <- data_reg %>%
  group_by(GROUP) %>%
  group_map(~ lm(MovementTime ~ ID_num, data = .x))
names(models) <- levels(data_reg$GROUP)

for (g in names(models)) {
  co <- coef(models[[g]])
  cat("Group", g, ": MT =", round(co[1], 3), "+", round(co[2], 3), "* ID\n")
}
```

Interpretation of the data

| Group | Intercept (a) | Slope (b) | Meaning of the slope |
|----|----|----|----|
| ap | 0.372 s | 0.165 s/bit | each extra bit of difficulty adds about 0.17 s |
| cp | 0.366 s | 0.123 s/bit | each extra bit adds about 0.12 s |
| pp | -0.259 s | 0.898 s/bit | each extra bit adds about 0.90 s |

The pp group adds around 0.9s for each difficlutly level. This figure is much larger compared to the figures of ap(0.17s) and cp(0.12s).
