## Run the ANOVA

```{r}
anova_results <- ezANOVA(
  data = data_clean,
  dv = .(MovementTime),# dependent variable
  wid = .(SUBJ),# to recognize each participant
  within = .(ID),# within-subject factor
  between = .(GROUP), # between-subject factor 
  detailed = FALSE
)

anova_results$ANOVA
```

ANOVA p-value:

We format the p-value to avoid scientific notation and see the full number. That way, it's easier to interpret the results.

```{r}
format(anova_results$ANOVA$p, scientific = FALSE, digits = 10)
```

Interpretation:

The ANOVA revealed significant main effects of GROUP and ID, as well as a significant GROUP × ID interaction, with all p-values below 0.01.

Detailed ANOVA results:

Effect of the GROUP: Movement Time is different between the three groups (p \< 0.01).

Effect of ID: Movement Time is different between the two IDs (p \< 0.01).

Interaction effect GROUPxID: The effect of ID on Movement Time depends on the GROUP (p \< 0.01). That is to say, Movement Time differs between the groups depending on the ID. For now, we do not know the direction of the effect, but we will see it in the graph below.

## Plot Movement Time as a Function of Index of Difficulty

```{r interaction plot}

interaction_plot_reference <- ggplot(data_clean) +
  aes(x = ID, y = MovementTime, color = GROUP) +
  # lines: one line type per group
  stat_summary(fun = mean, geom = "line",
               aes(group = GROUP, linetype = GROUP), alpha = 0.7) +
  # error bars: mean ± 0.215 s, same size for all groups
  stat_summary(fun.data = function(x) data.frame(y    = mean(x),
                                                 ymin = mean(x) - 0.215,
                                                 ymax = mean(x) + 0.215),
               geom = "errorbar", width = 0.25, alpha = 0.7) +
  # points: one shape per group
  stat_summary(fun = mean, geom = "point",
               aes(shape = GROUP), size = 1.5, alpha = 0.7) +
  labs(x = "ID", y = "Movement Time (s)")

show(interaction_plot_reference)
```

Interpretation:

From the ANOVA analysis, we already know that there is a significant interaction effect between GROUP and ID.
From the graph, we can see that Movement Time increases as the Index of Difficulty increases in all three groups. However, this increase is much stronger in the stroke patients group compared to the two other groups.
